Global liveability ranking

### 2022-07-24 inst/global_liveability_ranking.Rmd
not a useful analysis, reasons discussed

@@

[The global liveability ranking](https://en.wikipedia.org/wiki/Global_Liveability_Ranking)
shows where you would like to live.

@@

# A More coarse division

@@

```{r,plotfc}
plot(l,L-max(L),type="b")
```

@@

```{r}
glr
```

>>>>

_This analysis is essentially without value, see the very end for why_

(takes about an hour to process without cache)

@@

[The global liveability
ranking](https://en.wikipedia.org/wiki/Global_Liveability_Ranking)
shows the nicest places to live.

@@

# A coarser division

@@

```{r,plotfc}
plot(l,L-max(L),type="b")
abline(v=1)
```

@@

We need to replace each city with its country:

```{r,label=replacecity}
elastic
(jj <- list2nv(elastic,FALSE))
o_countries <- lapply(o, function(x){jj[names(jj) %in% x]})
(o_countries <- lapply(o_countries,as.vector))
```

We see that NZ and Australia are dominated so we should remove them:

```{r}
(o_countries <- lapply(o_countries,function(x){x[!(x %in% c("NZ","Australia","Japan"))]}))
```

But hang on, if we continue to remove dominated countries we
eventually remove every country that is not Austria.  So that was a big
fat waste of time.
